Analyzing Coopetition Strategies of Services within Communities

### 2012-11-26 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Updated Text

In figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low. For any reason our web services may need to stay in a particular community with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have increased the membership fee to the high amount of 5 units per run. Web services will need to pay 5 units on each iteration of tasks being offered. As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities. As reseults show the random and all compete strategies make web services bank deplete in no time. However our strategic coopetetive decision making process loses budget in a slower pace.

>>>>

In figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low. For any reason our web services may need to stay in a particular community with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have increased the membership fee to the high amount of 5 units per run. Web services will need to pay 5 units on each iteration of tasks being offered. As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a faster pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities. As results show the random and all compete strategies make web services bank deplete in no time. However our strategic coopetitive decision making process loses budget in a slower pace.
